IML Term project paper

### 2022-12-22 paper.rmd
Update paper.rmd
Pieniä korjauksia ja lisätty binary accuracy testidatalla logistiselle regressiolle, lassolle ja svm:lle

In order to reduce knitting time for the file, we will in this report instead of expressing the full R code to calculate the values, simply report the results we received. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|cc|}
\hline
Model type & loo-cv accuracy & loo-cv perplexity\\
\hline
Dummy model & 0 & 2.01\\
Logistic regression & 0.87 & 1.36\\
Naive Bayes & 0.81 & 152.85\\
LDA & 0.89 & 1.33\\
QDA & 0.85 & 6.34\\
SVM & 0.88 & 1.34\\
Lasso & 0.89 & 1.29\\
Random Forest & 0.89 & 1.35\\
\hline
\end{tabular}
\end{table}

@@

For our binary model, we ran the cross-validation 50 times, and received estimated ideal tuning parameters in interval [0.002073489, 0.04902743]. We first considered using the mean of these values as our choice of tuning parameter but as the values are rather dispersed (56% of values having tuning parameters $\lambda<0.005$ but then again, we have approximately 30% of parameter values that are larger than $0.01$), we should consider a different approach. Eventually, in order to bridge the gap between the two sets of values, we chose to prefer a slightly larger value than the median yet slightly lower than the mean for $\lambda$ and thus chose value $0.0075$ for the tuning parameter.

>>>>

In order to reduce knitting time for the file, we will in this report instead of expressing the full R code to calculate the values, simply report the results we received. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.87 & 1.36&0.84\\
Naive Bayes & 0.81 & 152.85&\\
LDA & 0.89 & 1.33&\\
QDA & 0.85 & 6.34&\\
SVM & 0.88 & 1.34&0.84\\
Lasso & 0.89 & 1.29&0.88\\
Random Forest & 0.89 & 1.35&\\
\hline
\end{tabular}
\end{table}

@@

Although we defined our result comparisons with loo-CV which has the benefit of returning consistent results when run several times, according to the course material [@book, p. 205-206], for example 5-or 10-fold cross-validation can give more accurate assessments of error rate. Thus, for our binary model we ran 10-fold cross-validation 50 times, and received estimated ideal tuning parameters in interval [0.002073489, 0.04902743]. We first considered using the mean of these values as our choice of tuning parameter but as the values are rather dispersed (56% of values having tuning parameters $\lambda<0.005$ but then again, we have approximately 30% of parameter values that are larger than $0.01$), we should consider a different approach. Eventually, in order to bridge the gap between the two sets of values, we chose to prefer a slightly larger value than the median yet slightly lower than the mean for $\lambda$ and thus chose value $0.0075$ for the tuning parameter.
